\chapter{ACTIVITY REPORT}
\section{Business Process in Company}
Business process that takes place in GSIT (Strategic Information Technology Group) in doing the process of production from start until it released are:
\begin{enumerate}
\item Requirement Assessment

Assessment of the need of latest technology required for BCA is typically done by Business Team or Fund Development Division  that doing the researches and compares the other bank technologies to emerge new business idea.

\item Sharing and Offering
The business idea then being discussed and proposed by GSIT in order to be applied in BCA. From that, the idea will be translated into other features or facilities in that application. Each feature is discussed in detailed until in its function and design.

\item IT Assessment

In this stage, GSIT will present its opinion about design that had been proposed and its technical implementation. Sometimes a very good design, not necessarily technically applicable. Depends on platform decision or operation system that will be used. Gathering requirements and making flow diagram from each feature also be done in this step.

\item Business Process

In making business process, GSIT is assisted by Business System Procedure (BSP) Division. GSIT and BSP will discuss together about each feature in detail, and repeating the gathering requirements process due to the possibility of increasing or more specific requirements is needed.

In this stage also, timeline or scheduling will be made together with Client and Application (CLA) Division to determined how long time to developing the application is needed. In making the schedule, usually deadline negotiation  is done in order to avoid over-time and also not too fast, so the product is really qualified and meet customer's desire.

\item Develop and Testing

The method that used in this developing stage is Scrum. Scrum is a framework for solving complex and adaptive problems, and at the same time, producing high value product with creativity and productivity. This technique makes the job become more organized and more detailed.

For instance, in an application to be built, there are 4 features in it. The team will work on one feature first, and then sent it to Client and Application Division for testing process. While the feature is being tested, GSIT worked on the second feature in order to do that feature testing immediately. And so on until all four feature had been completed. If in a feature there is a flaw or error during testing, it will be returned to GSIT for repairs.

After all features are done, it will be tested once more thoroughly (whole features testing) to check the perfection of built application. Then will be made certification and complementary documents before the application is released.

\item Publish

In publish stage, application that has been made is ready to be use. The application will be reviewed again about its function and the purpose of the application is built. If its an internal application, it will be given or distributed to internal company. But if its public or mass application, it will be published on Google Play Store and App Store.

\end{enumerate}
\section{Activities Performed According Learning Plan}
\subsection{Develop Mapping}
\subsection{Mapping review}
\paragraph{Review by PIC}
\paragraph{Review by script}
\subsection{Develop Workflow}
\subsection{SIT}
SIT is a process where we test the workflow by running the job we've already made.
\subsection{Data Regression}
\subsection{Implementation}
In this step, every process above has already been completed.